Suplementary information: Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-05-02 SupplementaryInformation.tex
Finish revision

\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
%\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaVCG}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

Many equivalent formulations have been proposed to obtain $\bm M$. For
a periodically
replicated multilayered system, the transfer matrix may be constructed
from the normal modes of the corresponding photonic crystal. These
modes are described by Bloch's
theorem, which reads in this case,
\begin{equation}
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{N}}=\bm M%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}}=e^{\pm iKD}%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}},  \label{Bloch}
\end{equation}%
where $D=z_{N}-z_{0}$ is the period, which corresponds to the actual
thickness of the multilayered system, and $\pm K$ is the 1D Bloch's
vector describing the propagation along $z$. Thus, $\Lambda_{\pm }=e^{\pm iKD}$ are
the eigenvalues of transfer matrix $\bm M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
}^{\pm }$ are the corresponding eigenvectors. Notice that $\det M=1$  exactly,
so the product of eigenvalues $\Lambda_{+}\Lambda_{-}=1$ and the
dispersion relation of the Bloch modes becomes
\begin{equation}
\cos KD=\frac{1}{2}\text{Tr}\,\bm M  \label{dispersion}
\end{equation}%
where T$\text{r}$ denotes the trace. \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIF1Squeme1DPC.pdf}
	\end{center}
	\caption{(a) Chirped-type photonic structure formed by two alternating
		materials $a$ and $b$, with refractive indices $n_{a}$ and $n_{b}$,
		thickness $d_{a}$ and $d_{b}$ that increases gradually
                according to some design scheme. We show schematically
                the  incident and reflected electric and magnetic
                fields, $\bm E_i$, $\bm H_i$,  $\bm E_r$, $\bm H_r$,
                their wavevectors $\bm k_i$ and $\bm k_r$, the right
                ($+$) and left ($-$) moving fields within each layer
                as well as their wavevectors $\bm k_\alpha^\pm$. (b)
                The multilayer system can be replaced by an
		effective layer within which supports right and left
                moving Bloch waves with wavevectors $\bm K^\pm=(\bm Q,
                K^\pm)$ and electric and magnetic field amplitudes
                $\bm E_\beta^\pm$ and $\bm H_\beta$. The projection of
              the wavevector unto the $xy$ plane is $\bm Q$ for all
              the waves, due to translational symmetry.}
	\label{Fig1}
\end{figure}

Now, consider a finite system made of $P$ periods, with thickness $PD$
and placed on a substrate. Even for the extreme $P=1$  case, the
optical properties of this system can be obtained by considering an incoming
wave from the ambient, a wave reflected to the environment, a wave
transmitted to the substrate, and two Bloch waves within the structure, one
moving up and other down, as show in Fig. \ref{Fig1}(b).

Hence, the continuity of $E_{\Vert }$ and $H_{\Vert }$ will produce two
equations at each interface, with which the four unknowns are obtained,
namely $r$, $t$ and the amplitudes of two Bloch's waves. In a finite system,
$K$ can be complex. Even in the presence of very little dissipation, Bloch's
waves should decay as they propagate. Thus, the eigenvalue of ascending mode
$\Lambda_{+}=e^{iKD}$ is identified as the one that obeys $|\Lambda_+|<1$, $%
\text{Im}K>0$, adding a negligible amount of dissipation if necessary to
avoid cases $|\Lambda_+|=1$.

From the eigenvalues $\Lambda_{\pm }$ of the transfer matrix, we may obtain
the corresponding eigenvectors $E_{\Vert }^{\pm }$ and $H_{\Vert }^{\pm }$
from Eq. (\ref{Bloch}), and from them, the corresponding surfaces impedances
\begin{equation}
Z^{\pm }=-\frac{M_{12}}{M_{11}-\Lambda_{\pm }},  \label{Z+-}
\end{equation}%
where $M_{ij}$ with $i=1,2$ and $j=1,2$ denote the elements of the transfer
matrix $M$. By writing the fields at $z_{0}$ and $z_{N}$ as a superposition
of the upward and downward propagating (or decaying) fields, $E_{\Vert
}^{\pm }=Z^{\pm }H_{\Vert }^{\pm }$, we can relate the fields at $z_{N}$ to
the fields at $z_{0}$ through a \emph{reconstructed} transfer matrix,
\begin{equation}
\begin{pmatrix}
E_{\Vert } \\
H_{\Vert }%
\end{pmatrix}%
_{z_{N}}=\tilde{M}%
\begin{pmatrix}
E_{\Vert } \\
H_{\Vert }%
\end{pmatrix}%
_{z_{0}},  \label{tilMEH}
\end{equation}%
where
\begin{equation}
\tilde{M}=\frac{1}{Z^{+}-Z^{-}}%
\begin{pmatrix}
Z^{+}e^{iKD}-Z^{-}e^{-iKD} & -2iZ^{+}Z^{-}\sin KD \\
2i\sin KD & Z^{+}e^{-iKD}-Z^{-}e^{iKD}%
\end{pmatrix}%
.  \label{tilM}
\end{equation}%
Finally, the explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
	\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
	_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
	_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
\end{equation}%
where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) have been chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization. As usual, the reflectance is given by $R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
the case of TM polarization.

@@

As the porosity contrast of the periods increases, the thickness of the structure
decreases and the average reflectance increases, as shown in table 1. For example,
you could have structures with a thickness of 10 $\mu$m and their average
reflectance greater than 90$\%$.

\begin{table}[tbph]
	\caption{ Design parameters obtained after the optimization of functions for maximum average reflectance and minimum thickness }
	\includegraphics[width=\textwidth]
	{SITableOptimized.pdf}
\end{table}

The mapping of the calculated reflectance of the structures designed with the
optimized parameters is shown in Fig. \ref{Fig2}. Here it is observed that all of
them have a PBG in the near infrared (NIR) region of the electromagnetic spectrum, i. e.,
structures designed from functions $f_{1}$ and $f_{3}$ with a porosity contrast of
$30/76\%$ have the highest PBG localized from 970 to 1370 nm, these are shown in
panels (a) and (c). \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIReflectanceVisNIR.pdf}
	\end{center}
	\caption{Calculated reflectance of the structures designed with the optimized parameters of $f_{1}$ (left), $f_{2}$ (center) and $f_{3}$ (right) and with the porosity contrasts of $30/76\%$ (upper panels) and $42/76\%$ (lower panels). The dotted lines limit the area of the PBG.}
	\label{Fig2}
\end{figure}

@@

Before showing the design of the structures formed by the stacking of sub-mirrors,
the transfer matrix trace of individual mirrors formed by one period (Fig.
\ref{Fig3}(a)) and six periods (Fig. \ref{Fig3}(b)) was calculated. The reflectance
of each mirror with its respective periods was also calculated (Figs. \ref{Fig3}(c)
and \ref{Fig3}(d)). Each mirror was designed to reflect a wavelength in the range of
400-3000 nm and the illumination range was the same. Additionally, the
$\text{Tr}|M|$ and $R(\lambda,\theta)$ were calculated for light with
  TE
polarization and $45^\circ$ of incidence. In Fig. \ref{Fig3}(d) it is shown that by using
mirrors that have 6 periods and designed to reflect at wavelengths greater than 1000
nm, they also reflect in a certain region of the visible spectrum. Then, to
reinforce the reflection of the electromagnetic waves in the visible, it is enough
to place a smaller number of periods. This is another reason for the increasing
number of periods in the 400 to 800 nm region. \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SITrazasyRefSE.pdf}
	\end{center}
	\caption{Calculated transfer matrix trace and reflectance of individual mirrors using ((a) and (c)) one period  and ((b) and (d)) six periods, respectively. Each mirror was tuned to a wavelength between 400 and 3000 nm. The calculations were made in the visible and NIR region and at 45${{}^\circ}$ of incidence.}
	\label{Fig3}
\end{figure}
\newpage

It is common to imagine that the stacking of the sub-mirrors is the following: that
the PBG of the second mirror begins at the edge of the PBG of the first mirror, the
third PBG that begins at the edge of the PBG of the second mirror, and so on until
the desired interval is completed. With this configuration, the reflectance
decreases at each intersection of the two PBGs. For example, Figs. \ref{Fig4}(a)
and \ref{Fig4}(b) show the calculated $R(\lambda, \theta)$ for the structures formed
by sub-mirrors that have one and six periods, respectively, using non-polarized
light. In these cases, the calculations do not show a PBG, or quasi-PBG. For this
reason, the $R_{Ave}(\lambda, \theta)$ was maximized through the percentage of
overlap of the PBGs of two consecutive sub-mirrors. In Fig. \ref{Fig3}(b) of the main
article the results obtained at the end of the optimization process are shown. The
calculated $R(\lambda, \theta)$ for the structures designed with 4 periods for each
sub-mirror and using the pattern described in the main article are shown in Figs.
\ref{Fig4}(c) and \ref{Fig4}(d) of this document, respectively. Here the overlap of
the two consecutive PBGs was optimized, being $72\%$ for the first case and $78\%$
for the last. Furthermore, the calculations indicate that the structures have a
quasi-PBG.

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{braket}
\usepackage{dcolumn}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
%\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaVCG}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

Many equivalent formulations have been proposed to obtain $\bm M$. For
a periodically
replicated multilayered system, the transfer matrix may be constructed
from the normal modes of the corresponding photonic crystal. These
modes are described by Bloch's
theorem, which reads in this case,
\begin{equation}
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{N}}=\bm M%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}}=e^{\pm iKD}%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}},  \label{Bloch}
\end{equation}%
where $D=z_{N}-z_{0}$ is the period, which corresponds to the actual
thickness of the multilayered system, and $\pm K$ is the 1D Bloch's
vector describing the propagation along $z$. Thus, $\Lambda_{\pm }=e^{\pm iKD}$ are
the eigenvalues of transfer matrix $\bm M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
}^{\pm }$ are the corresponding eigenvectors. Notice that $\det M=1$  exactly,
so the product of eigenvalues $\Lambda_{+}\Lambda_{-}=1$ and the
dispersion relation of the Bloch modes becomes
\begin{equation}
\cos KD=\frac{1}{2}\text{Tr}\,\bm M  \label{dispersion}
\end{equation}%
where T$\text{r}$ denotes the trace. \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIF1Squeme1DPC.pdf}
	\end{center}
	\caption{(a) Chirped-type photonic structure formed by two alternating
		materials $a$ and $b$, with refractive indices $n_{a}$ and $n_{b}$,
		thickness $d_{a}$ and $d_{b}$ that increases gradually
                according to some design scheme. We show schematically
                the  incident and reflected electric and magnetic
                fields, $\bm E_i$, $\bm H_i$,  $\bm E_r$, $\bm H_r$,
                their wavevectors $\bm k_i$ and $\bm k_r$, the right
                ($+$) and left ($-$) moving fields within each layer
                as well as their wavevectors $\bm k_\alpha^\pm$. (b)
                The multilayer system can be replaced by an
		effective layer within which supports right and left
                moving Bloch waves with wavevectors $\bm K^\pm=(\bm Q,
                \pm K)$ and electric and magnetic field amplitudes
                $\bm E_\beta^\pm$ and $\bm H_\beta$. The projection of
              the wavevector unto the $xy$ plane is $\bm Q$ for all
              the waves, due to translational symmetry and $K$ is
              obtained from Eq. \eqref{dispersion}.}
	\label{Fig1}
\end{figure}

Now, consider a finite system made of $P$ periods, with thickness $PD$
and placed on a substrate. Even for the extreme $P=1$  case, the
optical properties of this system can be obtained by considering an incoming
wave from the ambient, a wave reflected to the environment, a wave
transmitted to the substrate, and two Bloch waves within the structure, one
moving rightwards and other leftwards, as show in Fig. \ref{Fig1}(b). Hence, the
continuity of $E_{\Vert }$ and $H_{\Vert }$ yields two
equations at each interface, with which the four unknowns are obtained,
namely the reflection and transmission amplitudes $r$ and $t$, and the
amplitudes of the two Bloch's waves. In a finite system,
$K$ can be complex. Even in the presence of very little dissipation, Bloch's
waves should decay as they propagate. Thus, the eigenvalue of the right-moving mode
$\Lambda_{+}=e^{iKD}$ is identified as the one that obeys
$|\Lambda_+|<1$,
$\text{Im}\,K>0$, adding a negligible amount of dissipation if necessary to
avoid the case $|\Lambda_+|=1$. Then, $\Lambda_-=1/\lambda_+$

From the eigenvalues $\Lambda_{\pm }$ of the transfer matrix, we obtain
the corresponding eigenvectors $(E_{\Vert }^{\pm }, H_{\Vert }^{\pm
})$, and from them, the corresponding surfaces impedances, given by
\begin{equation}
Z^{\pm }=-\frac{M_{12}}{M_{11}-\Lambda_{\pm }},  \label{Z+-}
\end{equation}%
where $M_{ij}$ with $i=1,2$ and $j=1,2$ denote the elements of the transfer
matrix $\bm M$. By writing the fields at $z_{0}$ and $z_{N}$ as a superposition
of the upward and downward propagating (or decaying) fields, $E_{\Vert
}^{\pm }=Z^{\pm }H_{\Vert }^{\pm }$, we can relate the fields at $z_{N}$ to
the fields at $z_{0}$ through a \emph{reconstructed} transfer matrix,
\begin{equation}
\begin{pmatrix}
E_{\Vert } \\
H_{\Vert }%
\end{pmatrix}%
_{z_{N}}=\tilde{\bm M}%
\begin{pmatrix}
E_{\Vert } \\
H_{\Vert }%
\end{pmatrix}%
_{z_{0}},  \label{tilMEH}
\end{equation}%
where
\begin{equation}
\tilde{\bm M}=\frac{1}{Z^{+}-Z^{-}}%
\begin{pmatrix}
Z^{+}e^{iKD}-Z^{-}e^{-iKD} & -2iZ^{+}Z^{-}\sin KD \\
2i\sin KD & Z^{+}e^{-iKD}-Z^{-}e^{iKD}%
\end{pmatrix}%
,\label{tilM}
\end{equation}%
and its determinant is 1, even if numerical errors creep into the
calculation of the original matrix $\bm M$.
Finally, the explicit expressions for the optical coefficients are
\begin{equation}
r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
	\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
	_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
	_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
\end{equation}%
where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) have been chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization. As usual, the reflectance is given by $R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
the case of TM polarization.

@@

As the porosity contrast of the periods increases, the thickness of the structure
decreases and the average reflectance increases, as shown in table 1. For example,
you could have structures with a thickness of 10 $\mu$m with an average
reflectance greater than $90\%$.

\begin{table}[tbph]
	\caption{Optimized design parameters for different profile
          function classes for different porosity contrasts and some
          properties (number of periods, thickness and average
          reflectance) of the resulting structures.}
	\includegraphics[width=\textwidth]
	{SITableOptimized.pdf}
\end{table}

The calculated reflectance of the optimized structures
is shown in Fig. \ref{Fig2}. it is observed that they
have an ODB in the near infrared (NIR) region of the electromagnetic spectrum, i. e.,
structures designed from functions $f_{1}$ and $f_{3}$ with a porosity contrast of
$30/76\%$ have the widest ODB spanning from 970 to 1370 nm.

\begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIReflectanceVisNIR.pdf}
	\end{center}
	\caption{Calculated reflectance of the optimized structures
          with profile class $f_{1}$ (left), $f_{2}$
          (center) and $f_{3}$ (right) and with the porosities
          $30\%/76\%$ (upper panels) and $42\%/76\%$ (lower
          panels). The dotted lines limit the area of the ODB.}
	\label{Fig2}
\end{figure}

@@

We calclulated the trace of the transfer matrix of single Bragg mirrors formed by one period (Fig.
\ref{Fig3}(a)) and six periods (Fig. \ref{Fig3}(b)), as well as their
corresponding reflectance (Figs. \ref{Fig3}(c)
and \ref{Fig3}(d)), as a function of the design wavelength
$\lambda_{\text{dis}}$ and the wavelength of the illuminating light.
$\text{Tr}\,\bm M$ and $R(\lambda,\theta)$ were calculated for
TE polarized light incident at an angle of $45^\circ$.
Fig. \ref{Fig3}(d) shows that a
6-period mirror tuned to a  wavelength greater than 1000
nm, may also reflect in a certain region of the visible spectrum. Then, to
reinforce the reflection of the electromagnetic waves in the visible
a smaller number of periods is enough. This is another reason for increasing
number of periods in the 400 to 800 nm region.
\begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SITrazasyRefSE.pdf}
	\end{center}
	\caption{Calculated trace of the transfer matrix (left) and
          reflectance (right) of single Bragg mirrors one (top)
          and six (bottom) periods as a function of the design
          wavelength $\lambda_{\text{dis}}$ and the illumination
          wavelength $\lambda_{\text{ilum}}$.
          The calculations correspond to an incidence angle $\theta=45^\circ$.}
	\label{Fig3}
\end{figure}
\newpage

One strategy to design a wide band mirror could be stacking of the
sub-mirrors so that the leftmost edge of the band of one mirror begins
at the rightmost of the band of the previous mirror. However, with this
configuration, the reflectance
decreases where these band edges meet. For example, Figs. \ref{Fig4}(a)
and \ref{Fig4}(b) show the calculated $R(\lambda, \theta)$ for the structures formed
by sub-mirrors that have one and six periods, respectively, using non-polarized
light. In these cases, the calculations do not show a ODM, or quasi-ODM. For this
reason, we allowed succesive bands to overlap by some percentage
chosen to optimize the average reflectance $\braket{R}$. In Fig. \ref{Fig3}(b) of the main
article the results obtained at the end of the optimization process are shown. The
calculated $R(\lambda, \theta)$ for the structures designed with 4 periods for each
sub-mirror and using the pattern described in the main article are
shown in this document in Figs.
\ref{Fig4}(c) and \ref{Fig4}(d), respectively. Here the overlap of
the two consecutive PBGs was optimized, being $72\%$ for the first case and $78\%$
for the second. Furthermore, the calculations indicate that the structures have a
quasi-ODB.
